\section{Discussion}
% \paragraph{Change with pressure}
% When the gas pressure in the chamber increases, it causes an increase in the number of collisions between the electrons and the other plasma species. 
% As a result, the energy transferred from the electrons to the plasma species increases, causing a decrease in the electron temperature by increasing the gas pressure \cite{hassouba_analysis_2013}.
% Le meme paper a le bon resultat pour la densité aussi.

\subsection{Additional observations: Hysteresis}
An hysteresis was observed in several I-V curves acquired at high pressure and high tungsten filament current.
This is in fact caused by a contamination layer accumulated on the surface of the probe, a phenomenon which has been extensively studied by past studies and which is commonly modeled as a parallel capacitor and resistor, which introduce a phase difference between voltage and current.
The most detailed explanation we've found is in this 1976 paper by Oyama Koh-Ichiro
which also explains its formation and its cleaning.

\subsection{Comparisons with literature}
It was rather difficult to find other studies to compare our results with, as these sort of analysis are highly dependent on the experimental setup.
Nevertheless, we've found a couple of articles which do use a similar setup describing the same general behaviour of the temperature and density as a function of pressure (Hassouba and others and Li and others). 
We've also found this article by Kim and others with similar results concerning the radial profile of the plasma in the chamber.

\subsection{Possible further studies}
A setup allowing a probe to move in 2 or 3 dimensions would allow to make a complete profile of the plasma and would possibly show how the plasma falls of close to the edges, near the grill or near the heating filament.

A higher number of probes, as is often done in practice, would allow for a higher measurement precision or an analysis of the propagation of ion-acoustic waves. This Multi-Needle Langmuir probe is similar to the probe on the NorSat-1 satellite.

It would be interesting to use mixtures of different gas species and see how different [quantities] vary the properties of plasma.

TODO: put in conclusion?